\TitleFont Compressively sampled speech: How good is the recovery?

### 2020-07-03 Response to Reviewer Comments.tex

\documentclass[a4paper,12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[dvipsnames]{xcolor}
\parindent=0pt
\parskip=10pt

\begin{document}

\section*{Response to Reviewer Comments}

Dear Reviewer,

Thank you for reviewing our paper entitled ``Compressively sampled speech: How good is the recovery?'' and helping us improve our work. The following is our response to the points raised in your review. The texts in green show the changes we made in the paper.

\begin{enumerate}
	\item
		\begin{enumerate}
			\item \textbf{You are able to clearly present why using PESQ is advantageous over other metrics. However, in the introduction, I think discussion on how the algorithm works, how it is determined, etc. is lacking. Upon reading your paper, I just treated it as a blackbox algorithm. Adding a couple of sentences could prove helpful to the reader.}

			The algorithm of PESQ is quite long and complex, and we could not summarize it in the paper---even in diagram form---without going over the page limit. We refer the reader to the source material instead in Sec.~2.4, Paragraph 1:

			\begin{quotation}
				\textcolor{Green}{Due to the complexity of the algorithm, we refer the reader to Sec.~10 of the PESQ manual [8] for an in-depth discussion.}
			\end{quotation}
		\end{enumerate}

	\item
		\begin{enumerate}
			\item \textbf{Optional change: If possible, I would prefer it if you move the figures near where you mention them instead of all at the end.}

			From what we know, LaTeX automatically optimizes the positioning of elements in order to maximize space (and minimize page count). Thus, we opted to leave the positioning of the figures to the compiler.
		\end{enumerate}

	\item
		\begin{enumerate}
			\item \textbf{For future studies, can you try multiple audio files/samples? Maybe the results are specific for the audio sample (or explain why it is a good representative aside from being a random sample). However, I think the most important idea in this paper is using PESQ as a metric for CS-reconstructed audio signals so I think it can stand on its own without requiring more samples.}

			We conducted experiments on various audio files which also came from the TIMIT dataset and the results were consistent following the same procedure. This is most likely due to the consistency of the dataset as well, i.e., a number of unique sentences spoken by people with different accents and genders, all cleanly recorded at a rate of 16 kHz. The specific audio file used in this paper is simply a representative case based on all the previous experiments. For future studies, we can test signals from other datasets or record our own. You are correct regarding the important idea of the paper.

			\item \textbf{Change ``At face value'' to ``Visually,''. Remove ``we can immediately tell''.}

			By ``At face value'', we are referring to the value of PESQ. To avoid confusion, we have replaced the sentence to the following:

			\begin{quotation}
				\textcolor{Green}{By inspection of the PESQ value alone, we can tell that the reconstructed signal quality is slightly below average.}
			\end{quotation}

			\item \textbf{How do you determine ``slightly below average''?}

			The PESQ algorithm was modeled on subjective scoring systems. Such systems would ask people to rate an output signal, say, an integer from 1 to 5, given the input signal. In that case, 1 would correspond to bad, and 5 excellent. The output of PESQ is a float, but the authors still have opted to label the integer scores as 1.0 - bad, 2.0 - below average, 3.0 - average, 4.0 - good, 5.0 - perfect. The test signal yielded a PESQ value of 2.50, which is slightly below average.
		\end{enumerate}
\end{enumerate}

\end{document}

### 2020-07-03 main.tex
1st reviewer revisions

\begin{abstract}
\noindent
Modern signal acquisition technologies are made possible by the Nyquist-Shannon sampling theorem (NST). However, this paradigm is extremely wasteful as the signal is compressed before storing it by systematically discarding the imperceptible information. Compressive sensing (CS) aims to directly sense the relevant information. Current literature focus either on formulating more computationally-efficient algorithms, or methods which improve the reconstruction quality. In this paper, we quantify the reconstruction quality of compressively sampled speech with a perceptually intuitive metric---the Perceptual Evaluation of Speech Quality (PESQ)---and with the standard average segmental SNR (\snrseg). It is shown that the quality of recovery of compressively sampled speech evaluated using PESQ is dependent on the compression ratio, and independent of the number of subbands used to represent the signal in the spectrogram domain.

@@

\section{Introduction}\label{sec:intro}
Conventional sensing devices are based on the Nyquist-Shannon sampling theorem (NST), which states that given a signal's bandwidth, one can capture all the pertinent information about that signal if it is sampled at a rate

\begin{equation} \label{eq:nst}
	f_S \geq 2f_B
\end{equation}

\noindent where $f_B$ is the signal's highest frequency component, and $2f_B$ is known as the Nyquist rate. After this sampling process, the information is compressed by exploiting the signal's natural compressibility in some transform domain. For standard daily tasks, this tried-and-true method of sampling and systematically discarding the imperceptible information is acceptable for most applications. However, in certain situations when transmission bandwidth and/or storage comes at a premium, this process is highly wasteful. Cand\'{e}s et al. \cite{Candes2006} and Donoho et al. \cite{Donoho2006} independently pioneered compressive sensing (CS), which could directly sample the portions of a signal that would otherwise survive the compression stage in conventional sampling. In this new sampling paradigm, we consider the linear model of signal acquisition

@@

In other words, the signal vector $\vec{x} \in \mathbb{R}^n$ is correlated with the basis waveforms $\vec{a}_k$ to yield a compressed information vector $\vec{y} \in \mathbb{R}^m$, where $m \ll n$. This causes the task of recovering $\vec{x}$ from $\vec{y}$ impossible since there exist an infinite number of candidate solutions $\bm\hat{\vec{x}}$ which satisfy \eqref{eq:cesa}. This can be circumvented by enforcing sparsity and incoherence constraints \cite{Candes2008b} based on models of natural signals. The process of reconstruction can then be recast into a general minimization problem

@@

\subsection{Transforming to a sparse domain}\label{ssec:sparse}
The first requirement for CS is that a signal should be transformed to some domain where it can be represented sparsely. In the case of recorded speech, the most appropriate domain would be the modulation domain, otherwise known as its spectrogram. First, we define the length of the sampling window and the percent overlap between adjacent windows, and divide the signal into frames using this sliding window. We then multiply each frame by a window function, typically a Hann window, defined as

@@

\subsection{Reconstruction evaluation}\label{ssec:eval}
Reconstruction quality was evaluated using PESQ, which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS). The \snrseg~, defined as

@@

\section{Results and Discussion}
A test signal was chosen at random from the TIMIT corpus, specifically the \texttt{DR8/MJLN0/SA1.wav} file. This indicates that the speaker was from dialect region 8 (nomadic), was male with speaker code \texttt{JLN0}, and spoke sentence code \texttt{SA1}, which reads ``She had your dark suit in greasy wash water all year''. After downsampling, the signal was compressively sampled with a CR of 40\% using 1024 frames and 75\% frame overlap. The optimal regularization $\alpha$ was determined automatically via 5-fold cross validation, and the reconstruction result is shown in Fig.~\ref{fig:recovered}. Qualitative comparison in the temporal domain shows that the waveforms of the original and reconstructed are similar; in the modulation domain, the dynamic range appears to have decreased, but the dominant frequencies can still be observed. Evaluating the PESQ and \snrseg~yields values of 2.50 and 0.07, respectively. At face value, we can immediately tell from the PESQ that the reconstructed signal quality is slightly below average. However, this distinction cannot be made for the \snrseg~since its bounds are not clearly defined.

>>>>

\begin{abstract}
\noindent
Modern signal acquisition technologies are made possible by the Nyquist-Shannon sampling theorem (NST). However, this paradigm is extremely wasteful as the signal is compressed before storing it by systematically discarding imperceptible information. Compressive sensing (CS) aims to directly sense the relevant information. Current literature focus either on formulating more computationally-efficient algorithms, or methods which improve the reconstruction quality. In this paper, we quantify the reconstruction quality of compressively sampled speech with a perceptually intuitive metric---the Perceptual Evaluation of Speech Quality (PESQ)---and with the standard average segmental SNR (\snrseg). The quality of recovery of compressively sampled speech evaluated using PESQ is dependent on the compression ratio, and independent of the number of subbands used to represent the signal in the spectrogram domain.

@@

\section{Introduction}\label{sec:intro}
Conventional sensing devices are based on the Nyquist-Shannon sampling theorem (NST), which states that given a signal's bandwidth, one can capture all the pertinent information about that signal if it is sampled at a rate at least twice the signal's highest frequency component. After sampling, information is compressed by exploiting the signal's natural compressibility in some transform domain. For most applications, this tried-and-true method of sampling and systematically discarding the imperceptible information is acceptable. However, in situations when transmission bandwidth and/or storage comes at a premium, this process is highly wasteful. Cand\'{e}s et al. \cite{Candes2006} and Donoho et al. \cite{Donoho2006} independently pioneered compressive sensing (CS), which could directly sample the portions of a signal that would otherwise survive the compression stage in conventional sampling. In this new sampling paradigm, we consider the linear model of signal acquisition

@@

The signal vector $\vec{x} \in \mathbb{R}^n$ is correlated with the basis waveforms $\vec{a}_k$ to yield a compressed information vector $\vec{y} \in \mathbb{R}^m$, where $m \ll n$. This causes the task of recovering $\vec{x}$ from $\vec{y}$ infeasible since there exist an infinite number of candidate solutions $\bm\hat{\vec{x}}$ which satisfy \eqref{eq:cesa}. This can be circumvented by enforcing sparsity and incoherence constraints \cite{Candes2008b} based on models of natural signals. The process of reconstruction can then be recast into a general minimization problem

@@

\subsection{Transforming to a sparse domain}\label{ssec:sparse}
The first requirement for CS is that a signal should be transformed to a domain where it can be represented sparsely. In the case of recorded speech, the most appropriate domain would be the modulation domain, otherwise known as its spectrogram. First, we define the length of the sampling window and the percent overlap between adjacent windows, and divide the signal into frames using this sliding window. We then multiply each frame by a window function, typically a Hann window, defined as

@@

\subsection{Reconstruction evaluation}\label{ssec:eval}
Reconstruction quality was evaluated using PESQ, which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS). Due to the complexity of the algorithm, we refer the reader to Sec.~10 of the PESQ manual \cite{pesq} for an in-depth discussion.

The \snrseg~, defined as

@@

\section{Results and Discussion}
A test signal was chosen at random from the TIMIT corpus, specifically the \texttt{DR8/MJLN0/SA1.wav} file. This indicates that the speaker was from dialect region 8 (nomadic), was male with speaker code \texttt{JLN0}, and spoke sentence code \texttt{SA1}, which reads ``She had your dark suit in greasy wash water all year''. After downsampling, the signal was compressively sampled with a CR of 40\% using 1024 frames and 75\% frame overlap. The optimal regularization $\alpha$ was determined automatically via 5-fold cross validation, and the reconstruction result is shown in Fig.~\ref{fig:recovered}. Qualitative comparison in the temporal domain shows that the waveforms of the original and reconstructed are similar; in the modulation domain, the dynamic range decreased, but the dominant frequencies can still be observed. Evaluating the PESQ and \snrseg~yields values of 2.50 and 0.07, respectively. By inspection of the PESQ value alone, we can tell that the reconstructed signal quality is slightly below average. This distinction cannot be made for the \snrseg~since its bounds are not clearly defined.
